\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-11-12 tex/paper.tex
Added subsubsubsection functionality

\usepackage{fancyvrb}

@@

@@

TODO: Insert more systems here

\subsubsection{Perius}
Perius is the implementation that was done to solve the problem at hand at Uprise. This implementation is far from as 
efficient as the others in most aspects, but more efficient in some. As the implementation is built upon MongoDB as 
persistent storage and not a pure tree structure, single nodes can be fetched in O(1) but when querying for subtrees 
they need to be built first, which takes O(log(n)), where n is the number of nodes in the subtree.

@@

\section{Methods for determining\\implementation details}
This chapter introduces the different methods used to determine how the new system should be implemented, 
which DBMS it should use and how the estimation of long term scaling was done.

\section{Security of the system}
\subsection{Authorization}
\subsection{Audit logs}

\section{Resulting system}
\subsection{Persistent storage}
\subsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its internal storage 
format called BSON, which is very similar to JSON which the API is using. As the formats are similar, the process of 
marshalling and unmarshalling becomes quite easy between the core code, MongoDB instance and REST interface. 
The second reason was that if the system needs to scale in the future it is very easy to distribute MongoDB and if 
needed the system can easily be migrated to Reactive Mongo, which is an asynchronous and 
non-blocking driver for MongoDB and can therefore make the system scale even further~\cite{REACTIVEMONGO}.

\subsection{API}
REST was chosen as only basic CRUD operations needs to be performed and because the BSON format which is used in 
MongoDB is almost identical ~\cite{BSON} to the standardised JSON format which is used by RESTful services~\cite{JSON}.

@@

\subsection{Scalability}

>>>>

\usepackage{fancyvrb}
\usepackage{titlesec}

@@

% subsubsubsection
\titleclass{\subsubsubsection}{straight}[\subsection]

\newcounter{subsubsubsection}[subsubsection]
\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}
\renewcommand\theparagraph{\thesubsubsubsection.\arabic{paragraph}} % optional; useful if paragraphs are to be numbered

\titleformat{\subsubsubsection}
{\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
\titlespacing*{\subsubsubsection}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
    {3.25ex \@plus1ex \@minus.2ex}%
    {-1em}%
{\normalfont\normalsize\bfseries}}
\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
    {3.25ex \@plus1ex \@minus .2ex}%
    {-1em}%
{\normalfont\normalsize\bfseries}}
\def\toclevel@subsubsubsection{4}
\def\toclevel@paragraph{5}
\def\toclevel@paragraph{6}
\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
\makeatother

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

@@

TODO: Insert more systems here
\section{Implementation}
\subsection{Perius}
Perius is the implementation that was done to solve the problem at hand at Uprise. This implementation is far from as 
efficient as the others in most aspects, but more efficient in some. As the implementation is built upon MongoDB as 
persistent storage and not a pure tree structure, single nodes can be fetched in O(1) but when querying for subtrees 
they need to be built first, which takes O(log(n)), where n is the number of nodes in the subtree.

@@

\subsection{Methods for determining\\implementation details}
This chapter introduces the different methods used to determine how the new system should be implemented, 
which DBMS it should use and how the estimation of long term scaling was done.

\subsection{Resulting system}
\subsubsection{Persistent storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its internal storage 
format called BSON, which is very similar to JSON which the API is using. As the formats are similar, the process of 
marshalling and unmarshalling becomes quite easy between the core code, MongoDB instance and REST interface. 
The second reason was that if the system needs to scale in the future it is very easy to distribute MongoDB and if 
needed the system can easily be migrated to Reactive Mongo, which is an asynchronous and 
non-blocking driver for MongoDB and can therefore make the system scale even further~\cite{REACTIVEMONGO}.

\subsubsubsection{API}
REST was chosen as only basic CRUD operations needs to be performed and because the BSON format which is used in 
MongoDB is almost identical ~\cite{BSON} to the standardised JSON format which is used by RESTful services~\cite{JSON}.

@@

\subsection{Findings}
\subsubsection{Scalability}

\subsubsection{Security of the system}
\paragraph{Authorization}
\paragraph{Audit logs}
